Predicting Kamala Harris's Victory in the 2024 US Election

### 2024-11-02 paper/paper.qmd
Modify Reference

This study uses R packages [@citeR] to clean and analyz the dataset, including libraries from tidyverse [@tidyverse], ggplot2[@ggplot2], knitr[@knitr],usmap[@usmap], corrplot[@corrplot], arrow [@arrow].

@@

SurveyUSA is a privately held opinion research company that operates nationwide, across all 50 U.S. states. Since its founding, the company has conducted over 40,000 research projects, serving a client base of 400 organizations, including media outlets, corporations, non-profits, government agencies, and academic institutions. Known for its expertise in localized opinion research, SurveyUSA focuses on gathering data at the city, county, and regional levels. The company offers timely, cost-effective surveys tailored to meet specific client needs, distinguishing itself from larger global firms[@surveyusa_website].

@@

SurveyUSA uses a blend of probability and non-probability sampling methods. Some respondents are drawn from non-probability online panels, while others are recruited using probability-based telephone sampling. Responses are weighted based on the latest U.S. Census estimates for age, gender, ethnicity, and region, ensuring alignment with the target population. Questions and answer choices are rotated to reduce order bias, recency effects, and latency effects[@surveyusa_methodology].\

>>>>

This study uses R packages [@citeR] to clean and analyz the dataset, including libraries from tidyverse [@tidyverse], ggplot2 [@ggplot2], knitr [@knitr],usmap [@usmap], corrplot [@corrplot], arrow [@arrow].

@@

SurveyUSA is a privately held opinion research company that operates nationwide, across all 50 U.S. states. Since its founding, the company has conducted over 40,000 research projects, serving a client base of 400 organizations, including media outlets, corporations, non-profits, government agencies, and academic institutions. Known for its expertise in localized opinion research, SurveyUSA focuses on gathering data at the city, county, and regional levels. The company offers timely, cost-effective surveys tailored to meet specific client needs, distinguishing itself from larger global firms [@surveyusa_website].

@@

SurveyUSA uses a blend of probability and non-probability sampling methods. Some respondents are drawn from non-probability online panels, while others are recruited using probability-based telephone sampling. Responses are weighted based on the latest U.S. Census estimates for age, gender, ethnicity, and region, ensuring alignment with the target population. Questions and answer choices are rotated to reduce order bias, recency effects, and latency effects [@surveyusa_methodology].\
